---
title: "Homework 1"
author: "Rachel Tsong"
date: "2018-21-09"
output: github_document
---

# Problem 1

## Step 1
Load tidyverse 
``` {r}
library(tidyverse)
```

## Step 2
Create a random sample of size 10 from a uniform [0,5] distribution called "sample" 
``` {r} 
sample = runif(n = 10, min = 0, max = 5)
```

## Step 3
Create dataframe called "problem1_df"
``` {r dataframe}

vec_logical = sample > 2
vec_char = c("i", "made", "this", "character", "vector", "with", "length", "of", "ten", "yay")
vec_factor = factor(c("a", "a", "a", "a", "b", "b", "b", "b", "a", "b"))

problem1_df = tibble(
  sample,
  vec_logical,
  vec_char,
  vec_factor
  )

```
Here is the data frame:
``` {r echo = FALSE}
problem1_df
```

Can you take the mean?
-----------------------
* sample: yes, I can take the mean because it is a numerical vector
* vec_logical: yes, I can take the mean because R assigns TRUE and FALSE values of 1 and 0
* vec_char: no, I cannot take the mean because the vector is not numerical
* vec_factor: no, see above

## Step 4
Test what happens when you convert variables to a different type
```{r eval = FALSE}
as.numeric(vec_logical)
as.numeric(vec_char)
as.numeric(vec_factor)
```
What happens?
--------------
* vec_logical converted to 1/0 for T/F
* vec_char changed to NA 
* vec_factor converted to 1/2 for a/b


```{r}
as.numeric(as.factor(vec_char))
as.numeric(as.character(vec_factor))
```
What happens?
---------------
* Converting the character vector to a factor vector alphabetizes the vector, and converting this into a numeric vector assigns values to the cases based on this alphabetical order
* Converting the character vector to a factor vector to a numeric vector creates a vector where all cases become NA



# Problem 2

## Step 1
Create dataframe 
```{r}
x = rnorm(1000, 0 , 1)
y = rnorm(1000, 0 , 1)
sum_xy = x + y > 0
sum_xy_numeric = as.numeric(sum_xy)
sum_xy_factor = as.factor(sum_xy)

problem2_df = tibble(
  x,
  y,
  sum_xy,
  sum_xy_factor,
  sum_xy_numeric
)

```

Here is the data frame:
```{r echo = FALSE}
problem2_df
```

The size of the data set is `r dim(problem2_df)`. The variable x has a mean `r mean(x)` and median `r median(x)`. The proportion of cases for which the logical vector sum_xy is true is `r sum(sum_xy) * (1/1000)`.

## Step 2
Make scatterplots of y vs x
```{r echo = TRUE, fig.keep = 'all'}
plot_df = tibble(x, y)

ggplot(plot_df, aes(x = x, y = y, color = sum_xy)) + geom_point()

ggplot(plot_df, aes(x = x, y = y, color = sum_xy_numeric)) + geom_point()

ggplot(plot_df, aes(x = x, y = y, color = sum_xy_factor)) + geom_point()

```

For the logical and factor vector, the plots just have 2 colors for each of the 2 options, but for the numeric vector, the values are assigned to a color gradient.

## Step 3
Save first scatterplot
```{r}
ggsave("hw1_scatterplot.pdf", ggplot(plot_df, aes(x = x, y = y, color = sum_xy)) + geom_point())
```
