---
title: "Homework 1"
author: "Rachel Tsong"
date: "2018-21-09"
output: github_document
---

# Problem 1

## Step 1
Load tidyverse 
``` {r}
library(tidyverse)
```

## Step 2
Create a random sample of size 10 from a uniform [0,5] distribution called "sample" 
``` {r} 
sample = runif(n = 10, min = 0, max = 5)
```

## Step 3
Create dataframe called "problem1_df"
``` {r dataframe}

vec_logical = sample > 2
vec_char = c("i", "made", "this", "character", "vector", "with", "length", "of", "ten", "yay")
vec_factor = factor(c("a", "a", "a", "a", "b", "b", "b", "b", "a", "b"))

problem1_df = tibble(
  sample,
  vec_logical,
  vec_char,
  vec_factor
  )

```
Here is the data frame:
``` {r echo = FALSE}
problem1_df
```

## Step 4
Can you take the mean?
-----------------------
* sample: yes, I can take the mean because it is a numerical vector
* vec_logical: yes, I can take the mean because R assigns TRUE and FALSE values of 1 and 0
* vec_char: no, I cannot take the mean because the vector is not numerical
* vec_factor: no, see above

